{Working Principles Of Proof Assistants And Formalization Of Some Proofs in Agda}\\ {\large Supervisor: K.B manandar}\\

### 2025-06-01 proposal/formalization_of_proofs.tex
Literature curry-howard correospondance

\documentclass{article}
\usepackage{hyphenat}
\usepackage{booktabs}
\title{
    {Working Principles Of Proof Assistants And Formalization Of Some Proofs in Agda}\\
    {\large Supervisor: K.B manandar}\\

@@

Proofs or sometimes called the mathematical Proofs are at the foundation of all of mathematics and no mathematical reason are accepted unless they are proven by mathematical reasoning. The construction of proofs begins with initiation of terms, axioms and may bed dependent on previously proven

@@

Automated theorem proving but Interest in more interactive arrangement began later on when full automation became a much more difficult problem than supporting human guided proofs. (Harrison, Urban and Wiedijk ,2014) 
Auto-Math is considered probably the earliest of the interactive theorem provers, and was the first one of the theorem Provers to use Curry-howard isomorphism.

@@

Investigating the  Coq and the agda proof assistant and assessing the Logic that each proof assistant use and how the proof assistant use such logic to help check if the proof is valid.
We will also be inverstigating how to formalize some proofs in one of the proof assistant, and seeing how the logic holds in formalization of proofs.

@@

\section{Refrences}
\begin{enumerate}
    \item Sloane, N.J.A. (1998). Kepler's conjecture confirmed. Nature, 395(6701), pp.435\hyp{}436 doi:https://doi.org/10.1038/26609.
    \item Szpiro, G. (2003). Does the proof stack up? Nature, 424(6944), pp.12\hyp{}3,  doi:https://doi.org/10.1038/424012a
    \item Grami, A. (2022). Proof Methods. Elsevier eBooks, [online] pp.55\hyp{}65 doi:https://doi.org/10.1016/b978-0-12-820656-0.00004-6.
    \item Geuvers, H. (2009). Proof assistants: History, ideas and future. Sadhana, 34(1), pp.3\hyp{}25 doi:https://doi.org/10.1007/s12046-009-0001-5.
    \item Harrison, J, Urban, J. and Wiedijk, F. (2014). History of Interactive Theorem Proving. North-Holland, pp.135\hyp{}214.\\doi:https://doi.org/10.1016/B978-0-444-51624-4.50004-6
\end{enumerate}

>>>>

\documentclass{article}
\usepackage{hyphenat}
\usepackage{booktabs}
\usepackage{a4}
\title{
    {Working Principles Of Proof Assistants And Formalization Of Some Proofs in Agda}\\
    {\large Supervisor: K.B manandar}\\

@@

\indent{}
Proofs or sometimes called the mathematical Proofs are at the foundation of all 
of mathematics and no mathematical reason are accepted unless they are proven by mathematical reasoning.
The construction of proofs begins with initiation of terms, axioms and may bed dependent on previously proven

@@

 Interest in more interactive arrangement began much later on when full automated system became a very difficult problem than supporting human guided proofs.\\
AutoMath is considered possibly the earliest of human guided theorem provers which gave rise to various other systems of theorem prover and is the first program to use curry howard isomorphism for encoding of proofs (Harrison, Urban and Wiedijk ,2014) \\
Curry-Howard isomorphism states that any dertivation written in Intuitionstic Logic can be writing in their correosponding typable $ \lambda$\hyp{}terms. which means that proofs can be represented in programing terms, In short an isomorphism can be made between programs and logical proofs (Sørensen, M.H. and Urzyczyin, 2006).
Purely functional programming languages are based on $\lambda$-calculus (H.P Barendregt, 1990), this enables computability of forementioned derivations or proofs.

@@

In this project we will be investigating the  Coq and the agda proof assistant and assessing the Logic that each proof assistant use and how \the proof assistant use such logic to help check if the proof is valid.
We will also be inverstigating how to formalize some proofs in one of the proof assistant, and seeing how the logic holds in formalization of proofs.

@@

\section{Refrences}
\begin{enumerate}
    \item Sloane, N.J.A. (1998). Kepler's conjecture confirmed. Nature, 395(6701), pp.435\hyp{}436 doi:https://doi.org/10.1038/26609.
    \item Szpiro, G. (2003). Does the proof stack up? Nature, 424(6944), pp.12\hyp{}3,  doi:https://doi.org/10.1038/424012a
    \item Grami, A. (2022). Proof Methods. Elsevier eBooks, [online] pp.55\hyp{}65\\doi:https://doi.org/10.1016/b978-0-12-820656-0.00004-6.
    \item Geuvers, H. (2009). Proof assistants: History, ideas and future. Sadhana, 34(1), pp.3\hyp{}25 doi:https://doi.org/10.1007/s12046-009-0001-5.
    \item Harrison, J, Urban, J. and Wiedijk, F. (2014). History of Interactive Theorem Proving. North-Holland, pp.135\hyp{}214.\\doi:https://doi.org/10.1016/B978-0-444-51624-4.50004-6
    \item Sørensen, M.H. and Urzyczyin, P. (2006). The Curry-Howard isomorphism. Studies in Logic and the Foundations of Mathematics, pp.77\hyp{}101.\\doi:https://doi.org/10.1016/s0049-237x(06)80005-4.
    \item BARENDREGT, H.P. (1990). Functional Programming and Lambda Calculus. Formal Models and Semantics, pp.321\hyp{}363 \\doi:https://doi.org/10.1016/b978-0-444-88074-1.50012-3.
